Comprehensive Quality-Aware Automated Semantic Web Service Composition

### 2017-01-25 paper.tex
up

\subsection{Comparison Test with GP-based approach}\label{comparisonTestWithGP}
We compare a GP-based approach  \cite{ma2015hybrid} with our PSO method, where the individual is a tree structure transferred from a DAG employing unfolding techniques. We further mark all the tree nodes in the representation with its outgoing edges for semantic matchmaking quality, and those edges information are maintained correctly throughout the evolutionary process. At last, we evaluate both semantic matchmaking quality and QoS simultaneously using the discussed the comprehensive quality model to investigate the performances of both GP-based approaches and PSO-based approach. To make a fair comparison with our PSO approach that the same number of evaluations (3000 times) should be considered, we adjust the parameters settings for GP approach \cite{ma2015hybrid} to 30 individual for 100 generations.
\begin{table}[]
\centering
\caption{Mean fitness results for comparing GP-based approach}
\label{meanFitness}
\begin{tabular}{l|l|l}
\hline
\multicolumn{1}{c|}{Dataset} & PSO-based approach & GP-based approach  \\ \hline
WSC09 01                     &0.559207 $\pm$ 0.012780 $\uparrow$      &0.518411 $\pm$ 0.018470               \\ \hline
WSC09 02                     &0.470083 $\pm$  0.001106   &0.471594 $\pm$  0.002436 $\uparrow$           \\ \hline
WSC09 03                     & 0.559207 $\pm$ 0.012780 $\pm$ $\uparrow$  &0.552947 $\pm$ 0.007094            \\ \hline
WSC09 04                     & 0.468942 $\pm$ 0.001670 $\pm$ $\uparrow$  &0.442934 $\pm$ 0.010154            \\ \hline
WSC09 05                     & 0.469424 $\pm$ 0.000800 $\pm$ $\uparrow$  &0.256425 $\pm$ 0.038916            \\ \hline
\end{tabular}
\end{table}

\begin{table}[]
\centering
\caption{Mean time results for comparing GP-based approach}
\label{meanTime}
\begin{tabular}{l|l|l}
\hline
\multicolumn{1}{c|}{Dataset} & PSO-based approach & GP-based approach  \\ \hline
WSC09 01                     &12907 $\pm$ 8105      &5168 $\pm$ 520 $\downarrow$                \\ \hline
WSC09 02                     &292346 $\pm$  96727    &27483 $\pm$  3083 $\downarrow$          \\ \hline
WSC09 03                     & 12908 $\pm$ 8105   &28053 $\pm$ 3202 $\downarrow$           \\ \hline
WSC09 04                     & 6553640 $\pm$ 1468204   &540418 $\pm$ 186540 $\downarrow$            \\ \hline
WSC09 05                     & 1208193 $\pm$ 266916   &180408 $\pm$ 435247 $\downarrow$           \\ \hline
\end{tabular}
\end{table}

@@

>>>>

@@

\subsection{Comparison Test with GP-based approach}\label{comparisonTestWithGP}
We compare a GP-based approach  \cite{ma2015hybrid} with our PSO method, where the individual is a tree structure transferred from a DAG employing unfolding techniques. We further mark all the tree nodes in the representation with its outgoing edges for semantic matchmaking quality, and those edges information are maintained correctly throughout the evolutionary process. At last, we evaluate both semantic matchmaking quality and QoS simultaneously using the discussed the comprehensive quality model to investigate the performances of both GP-based approaches and PSO-based approach. To make a fair comparison with our PSO approach that the same number of evaluations (3000 times) should be considered, we adjust the parameters settings for GP approach \cite{ma2015hybrid} to 30 individual for 100 generations.

The Table \ref{meanFitness} shows the mean fitness values accomplished by two approaches and Table \ref{meanTime} shows the mean execution time required by them. We employ statistical analysis to test the significant differences in mean fitness value and execution time.  The results show that the PSO-based approach performs better in four of five tasks.

\begin{table}[]
\centering
\caption{Mean fitness results for comparing GP-based approach}
\label{meanFitness}
\begin{tabular}{l|l|l}
\hline
\multicolumn{1}{c|}{Dataset} & PSO-based approach & GP-based approach  \\ \hline
WSC09 01                     &0.559207 $\pm$ 0.012780 $\uparrow$      &0.518411 $\pm$ 0.018470               \\ \hline
WSC09 02                     &0.470083 $\pm$  0.001106   &0.471594 $\pm$  0.002436 $\uparrow$           \\ \hline
WSC09 03                     & 0.559207 $\pm$ 0.012780 $\pm$ $\uparrow$  &0.552947 $\pm$ 0.007094            \\ \hline
WSC09 04                     & 0.468942 $\pm$ 0.001670 $\pm$ $\uparrow$  &0.442934 $\pm$ 0.010154            \\ \hline
WSC09 05                     & 0.469424 $\pm$ 0.000800 $\pm$ $\uparrow$  &0.256425 $\pm$ 0.038916            \\ \hline
\end{tabular}
\end{table}

\begin{table}[]
\centering
\caption{Mean time results for comparing GP-based approach}
\label{meanTime}
\begin{tabular}{l|l|l}
\hline
\multicolumn{1}{c|}{Dataset} & PSO-based approach & GP-based approach  \\ \hline
WSC09 01                     &12907 $\pm$ 8105      &5168 $\pm$ 520 $\downarrow$                \\ \hline
WSC09 02                     &292346 $\pm$  96727    &27483 $\pm$  3083 $\downarrow$          \\ \hline
WSC09 03                     & 12908 $\pm$ 8105 $\downarrow$  &28053 $\pm$ 3202            \\ \hline
WSC09 04                     & 6553640 $\pm$ 1468204   &540418 $\pm$ 186540 $\downarrow$            \\ \hline
WSC09 05                     & 1208193 $\pm$ 266916   &180408 $\pm$ 435247 $\downarrow$           \\ \hline
\end{tabular}
\end{table}

We study the mean fitness value with the optimum for both PSO-based and GP-based approach over 30 independent runs. Fig. \ref{psovsgp} is an example of convergence rate performance in WSC09 03, which shows the behaviour of PSO-based approach manifests the characteristics of fast convergence and reaches a better-optimised solution, while the performance of GP is barely satisfactory.

\begin{figure}[h]
\centering
\fbox{\includegraphics[scale=.29]{psovsgp.pdf}}
 \caption{An example of comparing convergency rate from PSO and GP approaches for task 3}
 \label{psovsgp}
\end{figure}
